Why aren't significance tests commonly used for linear regression diagnostics?

### 2022-09-28 paper_comparison/paper_comparison/paper_comparison.Rmd
added susan and modifying captions

---
title: |
  Why aren't significance tests commonly used for linear regression diagnostics?
type: ARTICLE TEMPLATE
author:
  - name: Weihao Li
    affil: a
    email: weihao.li@monash.edu
  - name: Dianne Cook
    affil: a
    email: dicook@monash.edu
  - name: Emi Tanaka
    affil: a
    email: emi.tanaka@monash.edu
affiliation:
  - num: a
    address: |
      Department of Econometrics and Business Statistics, Monash University, Clayton, VIC, Australia
bibliography: paper.bib
abstract: |
  Abstract to fill.
keywords: |
  data visualization; visual inference; hypothesis testing; residual plots;
header-includes: |
  \usepackage{hyperref}
  \usepackage[utf8]{inputenc}
  \def\tightlist{}
  \newcommand*{\Perm}[2]{{}^{#1}\!P_{#2}}%
output: rticles::tf_article
editor_options: 
  chunk_output_type: inline
---

@@

  table_dat$f <- kableExtra::cell_spec(table_dat$f, bold = as.numeric(table_dat$f) < 0.05)
  table_dat$b <- kableExtra::cell_spec(table_dat$b, bold = as.numeric(table_dat$b) < 0.05)
  table_dat$s <- kableExtra::cell_spec(table_dat$s, bold = as.numeric(table_dat$s) < 0.05)

  table_dat %>%
  knitr::kable(col.names = c("Plot", "Departures", "Model structural", "Breusch-Pagan", "Shapiro–Wilk"),
               align = "llrrr",
               escape = FALSE,
               format = "latex",
               booktabs = TRUE, 
               caption  = 'Results of example residual plots given in Figure \\ref{fig:commondepartures} examined by the Model structural test (F-test), the Breusch-Pagan test and the Shapiro–Wilk test. P-values smaller than 0.05 are showed in bold.', 
               label = "example-residual-plot-table" )

@@

```{r first-example-lineup, fig.cap="An example lineup consists of 20 randomly placed residual plots, where 19 are null plots with data consistent with the null hypothesis, and one is the actual residual plot. Can you find the most different plot?"}
mod <- poly_model(include_z = TRUE, sigma = 1)
POLY_MODEL$plot_lineup(mod$gen_lineup(300, pos = 11), theme = theme_light(), remove_axis = TRUE, remove_grid_line = TRUE)
```

@@

### P-value calculation

>>>>

---
title: |
  Why aren't significance tests commonly used for linear regression diagnostics?
type: ARTICLE TEMPLATE
author:
  - name: Weihao Li
    affil: a
    email: weihao.li@monash.edu
  - name: Dianne Cook
    affil: a
    email: dicook@monash.edu
  - name: Emi Tanaka
    affil: a
    email: emi.tanaka@monash.edu
  - name: Susan VanderPlas
    affil: b
    email: susan.vanderplas@unl.edu
affiliation:
  - num: a
    address: |
      Department of Econometrics and Business Statistics, Monash University, Clayton, VIC, Australia
  - num: b
    address: |
      Department of Statistics, University of Nebraska, Lincoln, Nebraska, USA
bibliography: paper.bib
abstract: |
  Abstract to fill.
keywords: |
  data visualization; visual inference; hypothesis testing; residual plots;
header-includes: |
  \usepackage{hyperref}
  \usepackage[utf8]{inputenc}
  \def\tightlist{}
  \newcommand*{\Perm}[2]{{}^{#1}\!P_{#2}}%
output: rticles::tf_article
editor_options: 
  chunk_output_type: inline
---

@@

  table_dat$f <- kableExtra::cell_spec(table_dat$f, italic = as.numeric(table_dat$f) < 0.05)
  table_dat$b <- kableExtra::cell_spec(table_dat$b, italic = as.numeric(table_dat$b) < 0.05)
  table_dat$s <- kableExtra::cell_spec(table_dat$s, italic = as.numeric(table_dat$s) < 0.05)

  table_dat %>%
  knitr::kable(col.names = c("Plot", "Departures", "Model structural", "Breusch-Pagan", "Shapiro–Wilk"),
               align = "llrrr",
               escape = FALSE,
               format = "latex",
               booktabs = TRUE, 
               caption  = 'Statistical significance testing for departures from good residuals for plots in Figure \\ref{fig:commondepartures}. Shown are the $p$-values calculated for the conventional Model structural, the Breusch-Pagan and the Shapiro–Wilk tests. The good residual plot (A) is judged a good residual plot, as expected, by all tests. The non-linearity (B) is detected by all tests, as might be expected given the extreme structure.', 
               label = "example-residual-plot-table" )

@@

```{r first-example-lineup, fig.cap="Visual testing is conducted using a lineup, as in the example here. The residual plot computed from the observed data (plot 11, exhibiting non-linearity) is embedded among 19 null plots, where the residuals were simulated from a standard error model. Computing the $p$-value requires that the lineup be examined by a number of human judges, each asked to select the most different plot. A small $p$-value would result from a substantial number selecting plot 11."}
mod <- poly_model(include_z = TRUE, sigma = 1)
POLY_MODEL$plot_lineup(mod$gen_lineup(300, pos = 11), theme = theme_light(), remove_axis = TRUE, remove_grid_line = TRUE)
```

@@

### Calculating $p$-values

### 2022-09-28 paper_comparison/paper_comparison/paper_comparison.tex
added susan and modifying captions

\author{\name{Weihao Li$^{a}$, Dianne Cook$^{a}$, Emi Tanaka$^{a}$}
\affil{$^{a}$Department of Econometrics and Business Statistics, Monash
University, Clayton, VIC, Australia}
}

\thanks{CONTACT Weihao
Li. Email: \href{mailto:weihao.li@monash.edu}{\nolinkurl{weihao.li@monash.edu}}, Dianne
Cook. Email: \href{mailto:dicook@monash.edu}{\nolinkurl{dicook@monash.edu}}, Emi
Tanaka. Email: \href{mailto:emi.tanaka@monash.edu}{\nolinkurl{emi.tanaka@monash.edu}}}

@@

\caption{\label{tab:example-residual-plot-table}Results of example residual plots given in Figure \ref{fig:commondepartures} examined by the Model structural test (F-test), the Breusch-Pagan test and the Shapiro–Wilk test. P-values smaller than 0.05 are showed in bold.}
\centering
\begin{tabular}[t]{llrrr}
\toprule
Plot & Departures & Model structural & Breusch-Pagan & Shapiro–Wilk\\
\midrule
A & None & 0.434 & 0.133 & 0.728\\
B & Non-linearity & \textbf{0.000} & \textbf{0.000} & \textbf{0.039}\\
C & Heteroskedasticity & 0.378 & \textbf{0.000} & \textbf{0.000}\\
D & Non-normality & 0.667 & 0.736 & \textbf{0.000}\\
\bottomrule
\end{tabular}
\end{table}

@@

\begin{figure}
\includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/first-example-lineup-1} \caption{An example lineup consists of 20 randomly placed residual plots, where 19 are null plots with data consistent with the null hypothesis, and one is the actual residual plot. Can you find the most different plot?}\label{fig:first-example-lineup}
\end{figure}

@@

\hypertarget{p-value-calculation}{%
\subsubsection{P-value calculation}\label{p-value-calculation}}

>>>>

\author{\name{Weihao Li$^{a}$, Dianne Cook$^{a}$, Emi
Tanaka$^{a}$, Susan VanderPlas$^{b}$}
\affil{$^{a}$Department of Econometrics and Business Statistics, Monash
University, Clayton, VIC, Australia; $^{b}$Department of Statistics,
University of Nebraska, Lincoln, Nebraska, USA}
}

\thanks{CONTACT Weihao
Li. Email: \href{mailto:weihao.li@monash.edu}{\nolinkurl{weihao.li@monash.edu}}, Dianne
Cook. Email: \href{mailto:dicook@monash.edu}{\nolinkurl{dicook@monash.edu}}, Emi
Tanaka. Email: \href{mailto:emi.tanaka@monash.edu}{\nolinkurl{emi.tanaka@monash.edu}}, Susan
VanderPlas. Email: \href{mailto:susan.vanderplas@unl.edu}{\nolinkurl{susan.vanderplas@unl.edu}}}

@@

\caption{\label{tab:example-residual-plot-table}Statistical significance testing for departures from good residuals for plots in Figure \ref{fig:commondepartures}. Shown are the $p$-values calculated for the conventional Model structural, the Breusch-Pagan and the Shapiro–Wilk tests. The good residual plot (A) is judged a good residual plot, as expected, by all tests. The non-linearity (B) is detected by all tests, as might be expected given the extreme structure.}
\centering
\begin{tabular}[t]{llrrr}
\toprule
Plot & Departures & Model structural & Breusch-Pagan & Shapiro–Wilk\\
\midrule
A & None & 0.434 & 0.133 & 0.728\\
B & Non-linearity & \em{0.000} & \em{0.000} & \em{0.039}\\
C & Heteroskedasticity & 0.378 & \em{0.000} & \em{0.000}\\
D & Non-normality & 0.667 & 0.736 & \em{0.000}\\
\bottomrule
\end{tabular}
\end{table}

@@

\begin{figure}
\includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/first-example-lineup-1} \caption{Visual testing is conducted using a lineup, as in the example here. The residual plot computed from the observed data (plot 11, exhibiting non-linearity) is embedded among 19 null plots, where the residuals were simulated from a standard error model. Computing the $p$-value requires that the lineup be examined by a number of human judges, each asked to select the most different plot. A small $p$-value would result from a substantial number selecting plot 11.}\label{fig:first-example-lineup}
\end{figure}

@@

\hypertarget{calculating-p-values}{%
\subsubsection{\texorpdfstring{Calculating
\(p\)-values}{Calculating p-values}}\label{calculating-p-values}}
